Comparing variability across fMRI analysis software packages and numerical errors

### 2021-12-17 paper/paper.tex

We evaluated WT and BT variability for thresholded as well as unthresholded
group-level and subject-level t-statistics maps by computing the
standard deviation of t-statistic maps across pipelines or Fuzzy Libmath samples, respectively. For BT, we computed the standard deviation
across a given pair of tools \camille{standard dev with 2 samples ? cf. discussion on mattermost}.
For WT, we computed the standard deviation across the three
Fuzzy Libmath samples of a given tool. We computed WT variability for a pair of tools (A, B) as follows:
\begin{equation}
  \sigma_{WT(A,B)}^2 = \sigma_{WT(A)}^2 + \sigma_{WT(B)}^2,
  \label{eq:wt-pair}
\end{equation}
where $\sigma_{WT(.)}$ is the numerical variability for a given tool
and $\sigma_{WT(., .)}$ is the numerical variability for a pair of tools.

>>>>

We evaluated WT and BT variability for thresholded as well as unthresholded
group-level and subject-level t-statistics maps by computing the
absolute differences of t-statistic maps across pipelines or Fuzzy Libmath samples, respectively.
For BT, we computed the absolute differences across a given pair of tools.
For WT, we averaged the absolute differences between three pair combinations across the three
Fuzzy Libmath samples of a given tool. We computed WT variability for a pair of tools (A, B) as follows:
\begin{equation}
  WT(A,B) = \frac{WT(A) + WT(B)}{2},
  \label{eq:wt-pair}
\end{equation}
where $WT(.)$ is the numerical variability for a given tool
and $WT(., .)$ is the numerical variability for a pair of tools.
